\documentclass[11pt]{article}

% Encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Professional preprint style (reused from arxiv.sty)
\usepackage{arxiv}

% Content packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{natbib}

\usepackage{hyperref}
\usepackage{url}
\hypersetup{
  colorlinks=true,
  linkcolor=arxivaccent,
  citecolor=arxivaccent,
  urlcolor=arxivaccent,
  filecolor=arxivaccent,
  breaklinks=true,
}

% Code listing style (C / SQL / config)
\definecolor{codebg}{rgb}{0.95,0.95,0.97}
\definecolor{codegreen}{rgb}{0.0,0.5,0.0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{codeblue}{rgb}{0.0,0.0,0.7}
\lstdefinestyle{codestyle}{
    backgroundcolor=\color{codebg},
    basicstyle=\ttfamily\small,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    commentstyle=\color{codegreen},
    keywordstyle=\color{codeblue}\bfseries,
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    language=C,
    showstringspaces=false,
    numbers=left,
    numbersep=5pt,
    frame=single,
    rulecolor=\color{codegray},
    tabsize=4,
}
\lstset{style=codestyle}

\title{Fine-Grained Computation Offload for Event-Driven Applications}

\author{
  Bojie Li \\
  Pine AI
}

\date{}
\runningtitle{Fine-Grained Computation Offload for Event-Driven Applications}

\begin{document}
\maketitle

\begin{abstract}
Hardware accelerators now sit on the critical path of online serving. They include GPUs, TPUs, and
FPGAs, and increasingly \emph{remote} services such as hardware security modules, post-quantum
cryptography, and inference servers. A request is received, pre-processed, handed to the accelerator,
post-processed, and answered. While the accelerator works, the calling context stalls. For
\emph{fine-grained} offloads (microseconds to a few milliseconds), the classic responses both fall
short. A context switch to another thread, or a busy-wait, either wastes the CPU or adds a wakeup
latency comparable to the offload itself. The principled fix is to \emph{overlap} the offload with
other useful work, but this requires injecting concurrency into the application. The real question is
\emph{how much the application must change}.

We study this question across the landscape of real, off-the-shelf servers and find a
\emph{spectrum}. At one extreme, an \texttt{LD\_PRELOAD} M:N fiber runtime overlaps the offload with
\emph{zero} source modification. But it works only for thread-per-connection servers, and it hits
three hard walls: engines that synchronize below libc, managed runtimes that keep thread identity in
native thread-local storage, and workloads whose per-request CPU already exceeds the offload. At the
other extreme, a \emph{few lines} injected at the offload site overlap it through the application's
own concurrency, and this works everywhere. We evaluate ten production servers: Redis, nginx, memcached,
Node.js, Python/asyncio, Apache, Go, PostgreSQL, MariaDB, and HAProxy. Across them the change is
\textbf{18--112 lines added and 0--1 lines modified}. Measuring on real hardware only, with no
emulated latencies, real overlap lands at \textbf{$1.2$--$5\times$} on stock servers (and $17.3\times$
for the purpose-built transparent runtime). The win is bounded at \emph{both} ends. One bound is the
accelerator's own throughput: a large GPU offload saturates the device's memory bandwidth, so overlap
recovers its utilization rather than multiplying it. The other is the server's own overlap capacity: a
real latency-bound remote signer lifts the device ceiling but then hits the \texttt{asyncio}/GIL
executor at $3.5\times$. The dramatic order-of-magnitude wins that an unbounded offload model would
predict do not survive contact with real hardware. A simple model predicts both the speedup and the
code cost from two properties: the server's concurrency model and the offload weight relative to
per-request work. When the overlapped offload touches shared state, a transparent page-protection
conflict detector preserves correctness, which we validate on a stock Redis server. The result is a
practical recipe, and a predictive map, for hiding accelerator-offload latency in existing
event-driven servers.
\end{abstract}

\input{body}

\bibliographystyle{plainnat}
\bibliography{reference}

\end{document}
